results

### 2020-11-18 analysis/results.Rmd
add cor test snip / prop

>>>>

### citation

```{r}
hybrid_subject_19 <- hybrid_subject %>% 
  mutate(prop = oa /articles) %>%
  filter(issued_year == "2019", !is.na(percentile)
         , prop != 0) %>%
  distinct(issn, prop, percentile, snip, sjr)
```

spearman

```{r}
cor.test(hybrid_subject_19$prop, hybrid_subject_19$percentile, method = "spearman")
```

```{r}
ggplot(hybrid_subject_19, aes(prop, snip)) + geom_point(alpha = 0.2) + 
  geom_smooth(method = "loess", se = TRUE) +
  coord_cartesian(xlim = c(0., 0.7), ylim = c(0.5, 6)) +
  labs(x = "OA Uptake Rate", y = "SNIP") +
  theme_cowplot()
```
